---
title: "Analytical Plan for Prevalence of knee implant loosening in patients with prior surgery in a German hospital"
subtitle: 'DOCUMENT: SAP-2022-032-JF-v01'
author: '**From:** Felipe Figueiredo **To:** Jens Freitag'
date: "2022-11-09"
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    reference_docx: misc/style_SAP_en.docx
    toc: yes
# toc-title: "Sumário"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
options(scipen = 999)
library(pander)
library(knitr)
panderOptions('table.style', 'rmarkdown')
panderOptions('table.split.table', 160)
```

---

\newpage

**Analytical Plan for Prevalence of knee implant loosening in patients with prior surgery in a German hospital**

**Document version**

```{r history}
Version <- c("01")
Changes <- c("Initial version")
history <- cbind(Version, Changes)
colnames(history) <- c("Version", "Alterations")
# pander(history, split.cells = 70)
kable(history)
```

```{r cleaning, include=FALSE}
source("scripts/input.R", encoding = 'UTF-8')
```

---

# Abbreviations

- CI: confidence interval
- OR: odds ratio
- PR: prevalence ratio

# Context

## Objectives

Calculate the prevalence of knee prosthesis loosening in patients with prior history of knee surgery in Helios Klinikum Berlin-Buch, Germany.

## Hypotheses

# Data

## Raw data

The original data was already aggregated into counts of exposure and outcome.
No individual information was available on these patients (see Observations).

## Analytical dataset

N/A

# Study parameters

## Study design

This is a case-control study, based on hospital records.

## Inclusion and exclusion criteria

N/A

## Exposures

Exposure will be defined as having a previous knee surgery.

## Outcomes

**Specification of outcome measures** (Zarin, 2011):

1. (Domain) Knee arthroplasty
2. (Specific measurement) Implant loosening
3. (Specific metric) End value
4. (Method of aggregation) Frequency of implant loosening

**Primary outcome**

Cases will be defined as the patient experienced a knee implant loosening event.

## Covariates

N/A

# Statistical methods

## Statistical analyses

### Descriptive analyses

The counts of exposures and outcomes will be described in frequency and proportion (%), and summarized in a 2x2 contingency table.
Prevalence in exposed and unexposed will be reported.

### Inferential analyses

The distributions of participants' characteristics will be summarized in contingency tables.
The measures of association between exposure and outcome will be assessed with the PR.
The measure of effect will be assessed with the OR.
Both the point estimates and the CI around the estimates will be calculated using the Wald method.

### Statistical modeling

N/A

### Missing data

No missing data imputation will be performed.
All evaluations will be performed as complete case analyses.

## Significance and Confidence Intervals

All analyses will be performed using the significance level of 5%.
All significance hypothesis tests and confidence intervals computed will be
two-tailed.
<!-- left-tailed. -->
<!-- right-tailed. -->

## Study size and Power

N/A

## Statistical packages

This analysis will be performed using statistical software `R` version `r getRversion()`.

# Observations and limitations

**Aggregated sample data**

No individual-level data was available for this analysis.
This means that we cannot control for confounding either in regression models or stratified analyses.
It is recommended that this be reported as a limitation of the study, since it raises the risk of bias of the study.

**Recommended reporting guideline**

The adoption of the EQUATOR network (<http://www.equator-network.org/>) reporting guidelines have seen increasing adoption by scientific journals.
All observational studies are recommended to be reported following the STROBE guideline (von Elm et al, 2014).

# References

- **SAR-2022-032-JF-v01** -- Prevalence of knee implant loosening in patients with prior surgery in a German hospital
<!-- - Cohen, J. (1988). Statistical power analysis for the behavioral sciences (2nd Ed.). New York: Routledge. -->
- Zarin DA, et al. The ClinicalTrials.gov results database -- update and key issues. N Engl J Med 2011;364:852-60 (<https://doi.org/10.1056/NEJMsa1012065>).
- Gamble C, et al. Guidelines for the Content of Statistical Analysis Plans in Clinical Trials. JAMA. 2017;318(23):2337–2343 (<https://doi.org/10.1001/jama.2017.18556>).
- von Elm E, Altman DG, Egger M, Pocock SJ, Gøtzsche PC, Vandenbroucke JP; STROBE Initiative. The Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) Statement: guidelines for reporting observational studies. Int J Surg. 2014 Dec;12(12):1495-9 (<https://doi.org/10.1016/j.ijsu.2014.07.013>).

# Appendix

This document was elaborated following recommendations on the structure for Statistical Analysis Plans (Gamble, 2017) for better transparency and clarity.

## Associated analyses

This analysis is part of a larger project and is supported by other analyses, linked below.

**Implant failure rates in a knee prosthesis sub-population of the Helios Klinikum Berlin-Buch hospitals**

<https://philsf-biostat.github.io/SAR-2021-002-JF/>

## Availability

All documents from this consultation were included in the consultant's Portfolio.

<!-- The client has requested that this analysis be kept confidential until a future date, determined by the client. -->
<!-- All documents from this consultation are therefore not published online and only the title and year of the analysis will be included in the consultant's Portfolio. -->
<!-- After the agreed date is reached, the documents will be released. -->

<!-- The client has requested that this analysis be kept confidential. -->
<!-- All documents from this consultation are therefore not published online and only the title and year of the analysis will be included in the consultant's Portfolio. -->

The portfolio is available at:

<https://philsf-biostat.github.io/SAR-2022-032-JF/>
